Bayesian Sparsification Methods for Deep Complex-valued Networks

### 2020-06-16 paper/paper.tex
replaced two plots with single  better one

% testing the fx of the threshold
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
  \end{subfigure} \\
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__threshold__fine-tune.pdf}
  \end{subfigure}
  \caption{%
    Performance (smooth curve) and compression (curve with markers) of select experiments
    before (\textit{top}) and after (\textit{bottom}) fine-tuning.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

>>>>

% testing the fx of the threshold
\begin{figure}[!t]
  \centering
  \includegraphics[width=1\columnwidth]{figure__musicnet__threshold__C__DeepConvNet.pdf}
  \caption{%
    Effects of finetunig on performance-compression curves parametrized by $
      \tau\in \{\tfrac{k}2\colon k=-8..+8 \}
    $ for $
      C\in \{\tfrac1{20}, \frac1{200}\}
    $ in \eqref{eq:elbo_with_coef} during sparsification (sec.~\ref{sub:staging}).
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}
